Performing and evaluating graph-based clustering with rOpenScPCA

### 2024-11-14 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
WIP: delete extra text, and dont do stability with seurat

### Evaluating SCE clusters

```{r}
```

* Louvain algorithm
* Jaccard weighting
* 20 nearest neighbors
* Resolution of 1

Seurat parameters:
* louvain
* resolution of 0.8
*

There are a few common circumstances where you might encounter this:

```{r}
# Print the cluster column from the SCE object
head(colData(sce)$cluster)
```

In this section, we'll demonstrate how you can run the `rOpenScPCA` cluster evaluation functions on these clusters.

@@

```{r}
# Calculate clusters from an SCE object using default parameters
cluster_results_df <- calculate_clusters(sce)
```

>>>>

We do not recommend using `rOpenScPCA::calculate_stability()` on Seurat clusters due to differences in the underlying clustering approach between Seurat and the `bluster` package which `rOpenScPCA` uses.

### Evaluating ScPCA clusters

@@

```{r}
# Calculate clusters from an SCE object using default parameters
cluster_results_df <- calculate_clusters(sce)

# Calculate clusters from a Seurat object using default parameters
cluster_results_df <- calculate_clusters(seurat_obj)
```
